---
title: "**`A Stochastic Decision Tree to Support Rabies Control and Prevention Planning`**" 
author: David Anderson
date: "`r format(Sys.Date(), '%Y-%m-%d')`" 
output:  
  html_document:
    theme: cosmo 
    highlight: haddock
    toc: TRUE
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Libraries, message=FALSE, warning=FALSE, include=FALSE}
library(shiny)
library(shinyWidgets)
library(readr)
library(knitr)
library(dplyr)
library(tidyverse)
library(ggplot2)

# Source functions
source("R/HelperFun.R") # functions to help in simulations
source("R/decision_tree.R") # Decision Tree model & summary functions

```

```{css, echo=FALSE}

# format the html with CSS

h1, h2{
  text-align: center;
  font-family: Helvetica;
  font-weight: bold;
}

body{
  margin-top: 65px;
  font-family: Helvetica;
  font-weight: lighter;
  font-size: 12pt;
}

```
$~$

# Inputs

$~$

## Stochasticity
This decision tree uses binomial distributions when calculating stochasticity.
This method uses repeats in order to calculate mean and standard deviation values.
The more repeats used, the more "accurate" these values will be, however at the cost of longer loading times.

```{r echo=FALSE, message=FALSE, warning=FALSE}

numericInput("Repeats", "Number of repeats for stochasticty", value = 500, min = 1, step = 1)
RepeatList <- reactive({
  RepeatList <- 1:input$Repeats
  })

```

$~$

## Population Assumptions

```{r echo=FALSE, message=FALSE, warning=FALSE}

numericInput("Humans", "Human Population", value = 300000, min = 1, step = 1)

numericInput("HDR", "Human Dog Ratio", value = 8, min = 0.01, max = 100000, step = 0.01)


renderText({

  DogEst <- round(input$Humans/input$HDR) # Estimate dog population
  
  paste("This gives an estimated dog population of ", as.integer(DogEst), ".")
})

```

$~$

## Years

```{r echo=FALSE, message=FALSE, warning=FALSE}

numericInput("Years", "Years", value = 5, min = 1, step = 1)

numericInput("discount", "discount???", value = 0.03, min = 0, step = 0.01)

```

$~$

## Epidemialogical Assumptions

```{r echo=FALSE, message=FALSE, warning=FALSE}

numericRangeInput(inputId = "rabies_inc", label = "Rabies Incedence", value = c(0.0075, 0.0125), min = 0, max = 1, step = 0.0001)

numericRangeInput(inputId = "LR_range", label = "LR_range???", value = c(6.6,12.8), min = 0, step = 0.1)

numericInput("mu", "Persons bitten per rabid dog", value = 0.38, min = 0, step = 0.01)

numericInput("k", "Probability of infection without PEP (k?)", value = 0.14, min = 0, step = 0.01)

```

$~$

## PEP Factors

```{r echo=FALSE, message=FALSE, warning=FALSE}

numericInput("pStart", "pStart", value = 0.6666667, min = 0, max = 1, step = 0.0000001)

numericInput("pComplete", "pComplete", value = 0.3968254, min = 0, max = 1, step = 0.0000001)

numericInput("pDeath", "pDeath", value = 0.1660119, min = 0, max = 1, step = 0.0000001)

numericInput("pPrevent", "pPrevent", value = 0.986, min = 0, max = 1, step = 0.001)

```

$~$

## Cost Factors

```{r echo=FALSE, message=FALSE, warning=FALSE}

numericInput("full_cost", "Full Cost", value = 45, min = 0, step = 0.01)

numericInput("partial_cost", "Partial Cost", value = 25, min = 0, step = 0.01)

numericInput("campaign_cost", "Campaign Cost", value = 0, min = 0, step = 0.01)

```

$~$

# Outputs

```{r message=FALSE, warning=FALSE, include=FALSE}

DataFrame1 <- reactive({
  
  DataFrame1 <- decision_tree_ndraw(ndraw = input$Repeats, 
                       pop = input$Humans, HDR = input$HDR, 
                       horizon = input$Years, discount = input$discount,
                       rabies_inc = c(input$rabies_inc[1], input$rabies_inc[2]), 
                       LR_range = c(input$LR_range[1],input$LR_range[2]),
                       mu = input$mu, k = input$k,
                       pStart = input$pStart, pComplete = input$pComplete, pDeath = input$pDeath, pPrevent = input$pPrevent,
                       full_cost = input$full_cost, partial_cost = input$partial_cost, campaign_cost = input$campaign_cost)

})

DataFrame2 <- reactive({
  
  DataFrame1 <- decision_tree_ndraw(ndraw = input$Repeats, 
                       pop = input$Humans, HDR = input$HDR, 
                       horizon = input$Years, discount = input$discount,
                       rabies_inc = c(input$rabies_inc[1], input$rabies_inc[2]), 
                       LR_range = c(input$LR_range[1],input$LR_range[2]),
                       mu = input$mu, k = input$k,
                       pStart = input$pStart, pComplete = input$pComplete, pDeath = input$pDeath, pPrevent = input$pPrevent,
                       full_cost = input$full_cost, partial_cost = input$partial_cost, campaign_cost = input$campaign_cost)

})


```

$~$

## Outputs







